---
title: "Remote Sensing"
format: html
editor: visual
---

During my free time and from my Masters of Geomatics for Environmental Management (MGEM) at UBC, I have learned a range of remote sensing techniques and skills.

Below are some of those projects, current and past.

## Land Classification

The Remote Sensing course in MGEM taught me how to produce landscape classifications using a variety of supervised and unsupervised classification processes. Fascinated by different classification processes and the maps it produced, I extended this skill to produce a number of classified maps of various landscapes where Landsat and Copernicus satellite data was available. Generally my focus was with the Howe Sound Biosphere as it was part of my capstone project at UBC and is where I spend my time hiking, skiing and climbing. Below are some of the results of recent pixel classifications.

Supervised classification using RStoolbox package in R using LANDSAT 7 imagery of Howe Sound

```{r leaflet, echo=FALSE, warning=FALSE, message=FALSE}

library(leaflet)
library(terra)
library(raster)

LC_RStoolbox <- raster("C:/Users/lorsigno.stu/OneDrive - UBC/Desktop/Documents/Projects/Classification/HoweSound Classification/classified_map.tif")
LC_ArcGIS_RandomTrees <- raster("C:/Users/lorsigno.stu/OneDrive - UBC/Desktop/Documents/ArcGIS/Projects/MyProject/rf_hs_classification_1.tif")
LC_ArcGIS_DeepLearning <- raster("C:/Users/lorsigno.stu/OneDrive - UBC/Desktop/Documents/Projects/Classification/Deep Learning/HoweSound_DL_classification/hs_classification_deeplearning_test/hs_composite_DL_ClassifyP.tif")

HS_class_map <- leaflet(width = 600, height = 600)%>%
  
  # lets use some base imagery
  addProviderTiles("Esri.WorldImagery") %>%
  
  # add RStoolbox from R classification
  addRasterImage(LC_RStoolbox, 
                 # you can increase the allowable size of the rast here
                 maxBytes = 10 * 1024 *1024,
                 # provide a name for the layer
                 group = "LC_RStoolbox") %>%
  
  # add the ArcGIS Random Trees Wizard Classification
  addRasterImage(LC_ArcGIS_RandomTrees, 
                 # you can increase the allowable size of the rast here
                 maxBytes = 10 * 1024 *1024,
                 # provide a name for the layer
                 group = "LC_ArcGIS_RandomTrees") %>%
  
  # add the ArcGIS Deep Learning Classification
  addRasterImage(LC_ArcGIS_DeepLearning, 
                 #you can increase the allowable size of the rast here
                 maxBytes = 10 * 1024 *1024,
                 #provide a name for the layer
                 group = "LC_ArcGIS_DeepLearning") %>%

  
  #allow for layers to be toggles on/off by adding them to the layers control
  addLayersControl(baseGroups = c("LC-RStoolbox","LC-ArcGIS_RandomTrees", "LC-ArcGIS_DeepLearning")) %>%
  
  #add a legend
  #addRasterLegend(LC_RStoolbox, opacity = 1)%>%
  
  #add scale bar
  addScaleBar(position = c("bottomleft"))

```

```{r}
HS_class_map
```

Unsupervised classification using ArcGIS Pro

-   here i just want to insert either images from the land classification from ArcGIS or have interactive mapping

## Time Series Analysis

In this lab, I analyzed time series data in R by first working with MODIS NDVI data. I applied the BFAST algorithm to detect abrupt changes in vegetation—like logging events—that cause rapid declines in NDVI values. I then examined a 33‐year series of land cover maps from Landsat imagery, reclassifying the data into forested and non-forested areas to evaluate trends in forest loss and gain. Throughout the lab, I developed R code for data extraction, time series creation, and visualization, showcasing my practical skills in spatial and temporal analysis with packages such as terra, sf, and bfast.

## Burn Severity Analysis
